Predator clusters

### 2023-05-19 reports/04_pred_clus.qmd
Make cluster maps' color scheme match

ant_basemap(map_lim) +
  geom_sf(aes(color = pred_clust), pred_clust_sf, size = 2, shape = 15) +
  facet_wrap(~ Year) +
  scale_x_continuous(breaks = c(-60, -55)) +
  scale_y_continuous(breaks = c(-63, -62, -61, -60)) +
  coord_ant(map_lim) +
  theme(legend.position = "bottom")
```

@@

```{r}
#| label: env-loadings
#| eval: false

>>>>

ant_basemap(map_lim) +
  geom_sf(aes(color = pred_clust), pred_clust_sf, size = 2, shape = 15) +
  facet_wrap(~ Year) +
  scale_x_continuous(breaks = c(-60, -55)) +
  scale_y_continuous(breaks = c(-63, -62, -61, -60)) +
  scale_color_brewer(palette = "Dark2") +
  coord_ant(map_lim) +
  theme(legend.position = "bottom")
```

@@

```{r}
#| label: env-loadings
